The hydra and the rooster

### 2020-08-08 latex/chapter-hydras.tex
corrections on pdf file

  Infix "<" := lt2.

  (** reflexive closure of lt2 *)
  Let le2 := clos_refl _ lt2.
  Infix "<=" := le2.

@@

Like in Sect.~\ref{omega-case}, we prove the double inequality \texttt{m big\_h <= m small\_h < m big\_h}, which is impossible.

\subsubsection{Proof of the inequality \texttt{m small\_h < m big\_h}}

For proving the inequality  \texttt{m\_lt: m small\_h < m big\_h}, it suffices to
build a battle transforming \texttt{big\_h} into \texttt{small\_h}.

@@

\begin{Coqsrc}
Corollary m_lt : m small_h < m big_h.
\end{Coqsrc}

\subsubsection{Proof of the inequality \texttt{m big\_h <= m small\_h} }

The proof of the inequality \texttt{m big\_h <= m small\_h} is quite more complex than in Sect~\ref{omega-case}.  If we consider some pair $(i,j)$, where $i>0$, there exists an infinite number of
pairs stricly less than $(i,j)$, and there exists an infinite number of battles that start from
$\iota(i,j)$. In effect, at any configuration $\iota(k,0)$, the hydra can freely chose any replication number. Intuitively, the measure of such a hydra must be large enough for taking into account
all the possible battles issued from that hydra.
Let us give more technical details.

\begin{itemize}
\item The proof of the lemma \texttt{m\_ge : forall p : t,   p <= m (iota p)} uses well-founded induction on $p$, and not structural induction on natural numbers

@@

\begin{Coqsrc}
Lemma limit_is_lub : forall i p, 
   (forall j, (i,j) < p) <-> (S i, 0) <= p.  
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma m_ge : forall p : t,   p <= m (iota p).
Proof.
  intro p ; pattern p;
    apply  well_founded_induction with 
               (R := lt2) (1:= wf_lexico lt_wf lt_wf);
     intros (i,j) IHij (* rest of proof skipped *)
\end{Coqsrc}

\begin{Coqanswer}
  i, j : nat
  IHij : forall y : t, y < (i, j) -> y <= m (iota y)
  ============================
  (i, j) <= m (iota (i, j)) 
\end{Coqanswer}

@@

\begin{enumerate}
\item From \texttt{m\_lt}, we infer the strict inequality 
\texttt{m small\_h < m big\_h}
\item from \texttt{m\_ge}, we get \texttt{m big\_h <= m (iota (m big\_h)) = m small\_h} 
\end{enumerate}

>>>>

  Infix "o<" := lt2.

  (** reflexive closure of lt2 *)
  Let le2 := clos_refl _ lt2.
  Infix "o<=" := le2.

@@

Like in Sect.~\ref{omega-case}, we prove the double inequality \texttt{m big\_h o<= m small\_h o< m big\_h}, which is impossible.

\subsubsection{Proof of the inequality \texttt{m small\_h o< m big\_h}}

For proving the inequality  \texttt{m\_lt: m small\_h o< m big\_h}, it suffices to
build a battle transforming \texttt{big\_h} into \texttt{small\_h}.

@@

\begin{Coqsrc}
Corollary m_lt : m small_h o< m big_h.
\end{Coqsrc}

\subsubsection{Proof of the inequality \texttt{m big\_h o<= m small\_h} }

The proof of the inequality \texttt{m big\_h o<= m small\_h} is quite more complex than in Sect~\ref{omega-case}.  If we consider some pair $(i,j)$, where $i>0$, there exists an infinite number of
pairs stricly less than $(i,j)$, and there exists an infinite number of battles that start from
$\iota(i,j)$. In effect, at any configuration $\iota(k,0)$, the hydra can freely chose any replication number. Intuitively, the measure of such a hydra must be large enough for taking into account
all the possible battles issued from that hydra.
Let us give more technical details.

\begin{itemize}
\item The proof of the lemma \texttt{m\_ge : forall p : t,   p o<= m (iota p)} uses well-founded induction on $p$, and not structural induction on natural numbers

@@

\begin{Coqsrc}
Lemma limit_is_lub : forall i p, 
   (forall j, (i,j) o< p) <-> (S i, 0) o<= p.  
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma m_ge : forall p : t,   p o<= m (iota p).
Proof.
  intro p ; pattern p;
    apply  well_founded_induction with 
               (R := lt2) (1:= wf_lexico lt_wf lt_wf);
     intros (i,j) IHij (* rest of proof skipped *)
\end{Coqsrc}

\begin{Coqanswer}
  i, j : nat
  IHij : forall y : t, y o< (i, j) -> y o<= m (iota y)
  ============================
  (i, j) o<= m (iota (i, j)) 
\end{Coqanswer}

@@

\begin{enumerate}
\item From \texttt{m\_lt}, we infer the strict inequality 
\texttt{m small\_h o< m big\_h}
\item from \texttt{m\_ge}, we get \texttt{m big\_h o<= m (iota (m big\_h)) = m small\_h} 
\end{enumerate}

### 2020-08-08 latex/chapter-ks.tex
corrections on pdf file

s]\chapter{Inside \texorpdfstring{$\epsilon_0$}{epsilon0}: The Ketonen-Solovay machinery\label{ks-chapter}}
\label{chap:ketonen}
\index{Maths!Ketonen-Solovay machinery}

@@

Our proofs are  constructive and require no axioms: they are  closed terms of the CIC, and are mainly composed on function definitions and proofs of properties of these functions. 
They  share much theoretical material with Kirby and Paris', although they do not use any knowledge about Peano arithmetic nor model  theory.  The combinatorial arguments we use and implement
come from 
 an article by J.~Ketonen and R.~Solovay~\cite{KS81}, already  cited in the work
 by L.~Kirby et J.~Paris.% on the termination of Goodstein sequences and hydra battles~\cite{KP82}.
 Section $2$ of this article: ''A hierarchy of probably recursive functions'', contains a systematic study of \emph{canonical sequences}, which are closely related to
rounds of hydra battles.

@@

\label{lemma:canonS_LT}
\begin{Coqsrc}
Lemma canonS_LT i alpha :
  nf alpha -> alpha <> zero -> canonS alpha i <  alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma canonS_limit_strong (lambda : T1) : 
     nf lambda ->
     limitb lambda  ->
     forall beta, beta < lambda ->
                  {i:nat | beta < canonS lambda i}.

@@

\begin{Coqsrc}
Lemma LT_path_to (alpha beta : T1) :
  beta < alpha -> {s : list nat | path_to beta s alpha}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma path_to_LT beta s alpha :
  path_to beta s alpha -> nf alpha -> beta < alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_battle alpha beta :
    beta < alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

\section{A first proof of impossibility}

We have got all the tools for proving there is no variant bounded by some $\mu<\epsilon_0$ for proving the termination   of all battles. The proof we are going to show is a proof by contradiction. It  can
 be considered as a generalization of the
proofs described in  sections~\vref{omega-case} and \vref{omega2-case}.
We advise the reader to compare the three proofs step by step, lemma by lemma.

@@

\begin{Coqsrc}
Class BoundedVariant (B:Battle) :=
  {
    mu:T1 ;
    m: Hydra -> T1;
    mu_nf: nf mu;
    Hvar: Hvariant T1_wf B m;
    m_bounded: forall h, m h < mu
  }.
\end{Coqsrc}

@@

  Hypothesis m_decrease : forall  i h h',
        round_n i h h' -> m h' < m h.
\end{Coqsrc}

\begin{remark}
  The hypothesis \texttt{m\_decrease} is false in general, but is satisfied by
the  \texttt{free} and \texttt{standard} kinds of battles. This trick allows to 
``factorize'' our proofs our proofs of impossibility.
\end{remark}

@@

\begin{Coqsrc}
Lemma m_ge_0 alpha:  nf alpha -> alpha <= m (iota alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
    Corollary m_ge_generic : m big_h <= m small_h.
 \end{Coqsrc}

The (big) rest of the proof is dedicated to prove formally the converse inequality 
\texttt{m small\_h < m big\_h}.

@@

\begin{Coqsrc}
Lemma m_ge : m big_h <= m small_h.
  Proof.
    apply m_ge_generic.
   (* ... *)
\end{Coqsrc}

\item From the hypothesis \texttt{m\_bounded}, we have \texttt{m big\_h < mu}
\item By Lemma \texttt{LT\_to\_battle}, we get a (free) battle from
\texttt{big\_h = iota mu} to \texttt{small\_h = iota (m big\_h)}.

@@

\begin{Coqsrc}
Lemma m_lt : m small_h < m big_h.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_round_plus alpha beta :
    beta < alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary Cor12 (alpha : T1) :  nf alpha ->
         forall beta i n, beta  < alpha  ->
                (i < n)%nat ->
                 const_pathS i alpha beta ->
                 const_pathS n alpha beta.
Proof.
  transfinite_induction_lt alpha.
  (* (long) proof skipped *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary Cor12' (alpha : T1) :  nf alpha ->
         forall beta i n, (beta < alpha)%t1 ->
               (i <= n)%nat ->
               const_pathS i alpha beta ->
               const_pathS n alpha beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma Lemma2_6_1 (alpha : T1) :  
  nf alpha -> forall beta,  beta < alpha  ->
  {n:nat | const_pathS n alpha beta}.
Proof.
  transfinite_induction alpha.
  (* rest of proof skipped *)
\end{Coqsrc}

@@

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  < alpha ->
  {l:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

  Variables (alpha beta: T1) (n : nat).
  Hypotheses (Halpha: nf alpha) (Hpos : zero <  beta)
             (p : const_pathS n alpha  beta).
\end{Coqsrc}

@@

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  < alpha ->
  {j:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary  LT_to_standard_path  (alpha beta : T1) :
  beta < alpha ->
  {n : nat & {j:nat | standard_path (S n) alpha j beta}}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_standard_battle :
    forall alpha beta,
      beta < alpha ->
      exists n i,  battle standard  n (iota alpha) i (iota beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma m_ge : m big_h <= m small_h.
\end{Coqsrc}

>>>>

\chapter[The Ketonen-Solovay machinery]{Strolling inside \texorpdfstring{$\epsilon_0$}{epsilon0}: The Ketonen-Solovay machinery\label{ks-chapter}}
\label{chap:ketonen}
\index{Maths!Ketonen-Solovay machinery}

@@

Our proofs are  constructive and require no axioms: they are  closed terms of the CIC, and are mainly composed on function definitions and proofs of properties of these functions. 
They  share much theoretical material with Kirby and Paris', although they do not use any knowledge about Peano arithmetic nor model  theory.  The combinatorial arguments we use and implement
come from 
 an article by J.~Ketonen and R.~Solovay~\cite{KS81}, already  cited in the work
 by L.~Kirby et J.~Paris.% on the termination of Goodstein sequences and hydra battles~\cite{KP82}.
 Section $2$ of this article: ''A hierarchy of probably recursive functions'', contains a systematic study of \emph{canonical sequences}, which are closely related to
rounds of hydra battles. 
Nevertheless, they have the same global structure as the simple proofs described in
sections~\vref{omega-case} and \vref{omega2-case}. 
We invite the reader to compare the three proofs step by step, lemma by lemma.

@@

\label{lemma:canonS_LT}
\begin{Coqsrc}
Lemma canonS_LT i alpha :
  nf alpha -> alpha <> zero -> canonS alpha i o<  alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma canonS_limit_strong (lambda : T1) : 
     nf lambda ->
     limitb lambda  ->
     forall beta, beta o< lambda ->
                  {i:nat | beta o< canonS lambda i}.

@@

\begin{Coqsrc}
Lemma LT_path_to (alpha beta : T1) :
  beta o< alpha -> {s : list nat | path_to beta s alpha}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma path_to_LT beta s alpha :
  path_to beta s alpha -> nf alpha -> beta o< alpha.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_battle alpha beta :
    beta o< alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

\section{A  proof of impossibility}

We have got all the tools for proving there is no variant bounded by some $\mu<\epsilon_0$ for proving the termination   of all battles. The proof we are going to show is a proof by contradiction. It  can
 be considered as a generalization of the
proofs described in  sections~\vref{omega-case} and \vref{omega2-case}.

@@

\begin{Coqsrc}
Class BoundedVariant (B:Battle) :=
  {
    mu:T1 ;
    m: Hydra -> T1;
    mu_nf: nf mu;
    Hvar: Hvariant T1_wf B m;
    m_bounded: forall h, m h o< mu
  }.
\end{Coqsrc}

@@

  Hypothesis m_decrease : forall  i h h',
        round_n i h h' -> m h' o< m h.
\end{Coqsrc}

\begin{remark}
  The hypothesis \texttt{m\_decrease} is false in general, but is satisfied by
the  \texttt{free} and \texttt{standard} kinds of battles. This trick allows to 
``factorize'' our proofs  of impossibility.
\end{remark}

@@

\begin{Coqsrc}
Lemma m_ge_0 alpha:  nf alpha -> alpha o<= m (iota alpha).
\end{Coqsrc}

@@

\begin{Coqsrc}
    Corollary m_ge_generic : m big_h o<= m small_h.
 \end{Coqsrc}

The (big) rest of the proof is dedicated to prove formally the converse inequality 
\texttt{m small\_h o< m big\_h}.

@@

\begin{Coqsrc}
Lemma m_ge : m big_h o<= m small_h.
  Proof.
    apply m_ge_generic.
   (* ... *)
\end{Coqsrc}

\item From the hypothesis \texttt{m\_bounded}, we have \texttt{m big\_h o< mu}
\item By Lemma \texttt{LT\_to\_battle}, we get a (free) battle from
\texttt{big\_h = iota mu} to \texttt{small\_h = iota (m big\_h)}.

@@

\begin{Coqsrc}
Lemma m_lt : m small_h o< m big_h.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_round_plus alpha beta :
    beta o< alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary Cor12 (alpha : T1) :  nf alpha ->
         forall beta i n, beta  o< alpha  ->
                (i < n)%nat ->
                 const_pathS i alpha beta ->
                 const_pathS n alpha beta.
Proof.
  transfinite_induction_lt alpha.
  (* (long) proof skipped *)
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary Cor12' (alpha : T1) :  nf alpha ->
         forall beta i n, (beta o< alpha)%t1 ->
               (i <= n)%nat ->
               const_pathS i alpha beta ->
               const_pathS n alpha beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma Lemma2_6_1 (alpha : T1) :  
  nf alpha -> forall beta,  beta o< alpha  ->
  {n:nat | const_pathS n alpha beta}.
Proof.
  transfinite_induction alpha.
  (* rest of proof skipped *)
\end{Coqsrc}

@@

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  o< alpha ->
  {l:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

  Variables (alpha beta: T1) (n : nat).
  Hypotheses (Halpha: nf alpha) (Hpos : zero o<  beta)
             (p : const_pathS n alpha  beta).
\end{Coqsrc}

@@

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  o< alpha ->
  {j:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Corollary  LT_to_standard_path  (alpha beta : T1) :
  beta o< alpha ->
  {n : nat & {j:nat | standard_path (S n) alpha j beta}}.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_standard_battle :
    forall alpha beta,
      beta o< alpha ->
      exists n i,  battle standard  n (iota alpha) i (iota beta).
\end{Coqsrc}

@@

\begin{Coqsrc}
 Lemma m_ge : m big_h o<= m small_h.
\end{Coqsrc}

### 2020-08-08 latex/chapter-large-sets.tex
corrections on pdf file

\begin{Coqsrc}
canonS_LT:
  forall (i : nat) (alpha : T1),
  nf alpha -> alpha <> zero -> canonS alpha i < alpha.

@@

\begin{Coqsrc}
Remark H_non_mono1 :
  ~ (forall alpha beta k, (alpha <= beta)%e0 ->
                          (H_ alpha k <= H_ beta k)%nat).
Proof.
 intros H ;specialize (H 42 omega 3).
 assert (H0 :(42 <= omega)%e0) by (repeat split; auto).  
 apply H in H0; rewrite H_Fin, H_omega  in H0; lia.
Qed.
\end{Coqsrc}

@@

\begin{Coqanswer}
The command has indeed failed with message:
In environment
alpha : E0
notlimit : Limitb alpha = false
nonzero : alpha <> Zero
i : nat
F_ : forall x : E0, nat -> x < alpha -> nat
The term "F_ (Pred alpha) ?x" has type "Pred alpha < alpha -> nat"
while it is expected to have type "Pred alpha < alpha -> Pred alpha < alpha"
(cannot unify "nat" and "Pred alpha < alpha").
\end{Coqanswer}

@@

\begin{Coqsrc}
Lemma Propp284 : forall alpha beta : E0, 
   beta < alpha -> dominates (F_ alpha) (F_ beta).
\end{Coqsrc}

>>>>

\begin{Coqsrc}
canonS_LT:
  forall (i : nat) (alpha : T1),
  nf alpha -> alpha <> zero -> canonS alpha i o< alpha.

@@

\begin{Coqsrc}
Remark H_non_mono1 :
  ~ (forall alpha beta k, (alpha o<= beta)%e0 ->
                          (H_ alpha k <= H_ beta k)%nat).
Proof.
 intros H ;specialize (H 42 omega 3).
 assert (H0 :(42 o<= omega)%e0) by (repeat split; auto).  
 apply H in H0; rewrite H_Fin, H_omega  in H0; lia.
Qed.
\end{Coqsrc}

@@

\begin{Coqanswer}
The command has indeed failed with message:
In environment
alpha : E0
notlimit : Limitb alpha = false
nonzero : alpha <> Zero
i : nat
F_ : forall x : E0, nat -> x o< alpha -> nat
The term "F_ (Pred alpha) ?x" has type "Pred alpha o< alpha -> nat"
while it is expected to have type "Pred alpha o< alpha -> Pred alpha o< alpha"
(cannot unify "nat" and "Pred alpha o< alpha").
\end{Coqanswer}

@@

\begin{Coqsrc}
Lemma Propp284 : forall alpha beta : E0, 
   beta o< alpha -> dominates (F_ alpha) (F_ beta).
\end{Coqsrc}

### 2020-08-08 latex/chapter-ordinals.tex
correction on pdf file
corrections on pdf file

Definition on_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.
Infix "<" := on_lt : ON_scope.

@@

Infix "<=" := on_le : ON_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example ex1 : inl 7 < inr 0.
Proof. constructor. Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example ex1' : fin 7 < omega.
Proof. constructor. Qed.
\end{Coqsrc}

\label{warning:coercions}
\index{Coq!Techniques!Coercions} 
\begin{remark}
Beware of coercions and notation scopes!

Let us consider the following goal:

\begin{Coqsrc}
 Goal (6 < 8).
 auto with arith.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 9)

  ============================
  6 < 8
\end{Coqanswer}

Please keep in mind that the current notation scope interprets the infix \texttt{``<''} as the predicate \texttt{Omega\_plus\_omega.lt} and not \texttt{Nat.lt}. More,  the coercion mechanism converts the terms \texttt{6:nat} [resp. \texttt{8:nat} ]
into \texttt{inl 6} [resp. \texttt{inl 8}].  So, the initial goal is correctly interpreted by \coq{}, but not as an inequality between two natural numbers.

\begin{Coqsrc}
Set Printing All.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 337)

  ============================
  @on_lt nat Peano.lt Nat.compare Omega (S (S (S (S (S (S O))))))
    (S (S (S (S (S (S (S (S O))))))))
\end{Coqanswer}

Anyway, the initial goal is provable, using \texttt{le\_AsB} first constructor.

\begin{Coqsrc}
  constructor; auto with arith.
Qed.
\end{Coqsrc}

@@

\begin{itemize}
\item A \emph{least} element is a minorant (in the large sense) of the full set  on $A$,
\item $y$ is a \emph{successor} of $x$ if $x<y$ and there is no element between $x$ and $y$,
\item $x$ is a \emph{limit} if $x$ is not a least element, and for any $y$ such that $y<x$,
 there exists some $z$ such that $y<z<x$.
\end{itemize}

@@

\index{Projects}
\begin{project}
Define in \coq{} the product of two ordinal notations $N_A$ and $N_B$.
If $A$ [resp. $B$] is the underlying type of $N_A$ [resp. $N_B$], the
product \texttt{ON\_mult $N_A$ $N_B$} is implemented over the cartesian product $B\times A$ (with the lexicographic ordering).

@@

For instance, let us take $N_A=\texttt{Omega}$, and take $\alpha=(4,4,2,1,0)$,
 $\beta=(4,3,3,3,3,3,2)$, and $\gamma=(5)$. Then $\beta<\alpha<\gamma$.

In contrast the list $(5,6,3,3)$ is not non-increasing (\emph{i.e.} sorted w.r.t. $\geq$), so it is not to be considered.

>>>>

Definition on_lt {A:Type}{lt: relation A}
           {compare : A -> A -> comparison}
           {on : ON lt compare} := lt.
Infix "o<" := on_lt : ON_scope.

@@

Infix "o<=" := on_le : ON_scope.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example ex1 : inl 7 o< inr 0.
Proof. constructor. Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Example ex1' : fin 7 o< omega.
Proof. constructor. Qed.
\end{Coqsrc}

% \label{warning:coercions}
% \index{Coq!Techniques!Coercions} 
% \begin{remark}
% Beware of coercions and notation scopes!
% Let us consider the following goal:

% \begin{Coqsrc}
%  Goal (6 o< 8).
%  auto with arith.
% \end{Coqsrc}

% \begin{Coqanswer}
% 1 subgoal (ID 9)

%   ============================
%   6 o< 8
% \end{Coqanswer}

% Please keep in mind that the current notation scope interprets the infix \texttt{``<''} as the predicate \texttt{Omega\_plus\_omega.lt} and not \texttt{Nat.lt}. More,  the coercion mechanism converts the terms \texttt{6:nat} [resp. \texttt{8:nat} ]
% into \texttt{inl 6} [resp. \texttt{inl 8}].  So, the initial goal is correctly interpreted by \coq{}, but not as an inequality between two natural numbers.

% \begin{Coqsrc}
% Set Printing All.
% \end{Coqsrc}

% \begin{Coqanswer}
% 1 subgoal (ID 337)

%   ============================
%   @on_lt nat Peano.lt Nat.compare Omega (S (S (S (S (S (S O))))))
%     (S (S (S (S (S (S (S (S O))))))))
% \end{Coqanswer}

% Anyway, the initial goal is provable, using \texttt{le\_AsB}'s first constructor.

% \begin{Coqsrc}
%   constructor; auto with arith.
% Qed.
% \end{Coqsrc}

% \end{remark}
%

@@

\begin{itemize}
\item A \emph{least} element is a minorant (in the large sense) of the full set  on $A$,
\item $y$ is a \emph{successor} of $x$ if $x<y$ and there is no element between $x$ and $y$,
\item $x$ is a \emph{limit} if $x$ is not a least element, and for any $y$ such that $yo<x$,
 there exists some $z$ such that $y<z<x$.
\end{itemize}

@@

\index{Projects}
\label{exo:ON-mult}
\begin{project}
Define in \coq{} the product of two ordinal notations $N_A$ and $N_B$.
If $A$ [resp. $B$] is the underlying type of $N_A$ [resp. $N_B$], the
product \texttt{ON\_mult $N_A$ $N_B$} is implemented over the cartesian product $B\times A$ (with the lexicographic ordering).

@@

For instance, let us take $N_A=\texttt{Omega}$, and take $\alpha=\langle 4,4,2,1,0\rangle$,
 $\beta=\langle 4,3,3,3,3,3,2\rangle$, and $\gamma=\langle 5\rangle$. Then $\beta<\alpha<\gamma$.

In contrast the list $\langle5,6,3,3\rangle$ is not non-increasing (\emph{i.e.} sorted w.r.t. $\geq$), so it is not to be considered.
